On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-11-27 MS.tex
Dataset change for Herault et al 1995 Reviewer comments added

\mstype{Research Article}
\runninghead{Influence of traits on growth changes with size}
\keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 235/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate has often been seen as a central element of its ecological strategy, and as ultimately linked to its traits. Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of traits to predict growth.

\item We propose that traits should influence growth in a way that depends on the size of individual plants. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations). To capture the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: seedling, sapling and adult.

\item Results were consistent with predictions. Specific leaf area was correlated with relative growth rate (RGR) in seedling but not in adult plants. Correlations of RGR with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.

\item Synthesis: We show how trait-growth correlations change in a predictable way with plant size. Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.

@@

The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring. An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}. From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The ``leaf economic spectrum'' \citep{Wright:2004jb} and the ``wood economic spectrum'' \citep{Chave:2009iy} reflect tissue construction costs (for leaf area and for wood volume respectively), trading off with rates of tissue turnover or mortality. It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}. Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, the correlation has mostly been much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}. Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}. At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see section ``Theoretical expectations''). While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.

In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass = SM) to investigate:
\begin{enumerate}
  \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') derived from a recently developed mechanistic model \citep{Falster:2011ii}?
\end{enumerate}
We gathered correlation coefficients between traits and growth from studies that gave explicit information about the size or stage of the plants. While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes. We used plant stage (i.e. seedling, sapling and adult) as a surrogate for the effects of plant size. We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.

@@

\textbf{H4: The relationship between SM and relative growth rate is negative in seedlings, but weakens with increasing size.}

@@

We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is measured. It is uncertain how much this might translate to faster growth in low light.

\textbf{Effect on absolute and relative growth rates}
Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR). According to the growth model, the predicted relationship between growth and SM in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}). The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$. For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used.

@@

We aimed to identify studies that measured the correlation between five prominent functional traits (SLA, WD, Aarea, Hmax and SM) and a growth measurement across species. Our literature search was conducted in two phases.

@@

The Google Scholar database was searched using a range of Boolean search terms for SLA and WD: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''). This keyword search in Google Scholar returned approx. 18900 papers, from which we took the first 750 items when ranked by ``relevance''.
These papers were examined in addition to those discovered in Phase 1. In addition, we gleaned data from other sources, using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

Overall, we recorded coefficient correlations for a list of 19 traits (Fig. \ref{fig:fig1}): the five for which we had prior expectations, plus 14 others commonly used in the trait literature. SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. SM and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}. According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits was captured by a search on SLA and WD.

@@

In addition to the chosen criteria for the meta-analyses, the growth measurement used (relative growth rate-RGR or absolute growth rate-AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Thus we stratified the data set into two subsets: one including only studies on RGR, under unstressed conditions and measuring a correlation coefficient at least across 10 species (’ideal’ dataset), and the other set including studies under all conditions (’complete’ dataset). We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e. seed stage), or Hmax (i.e. adult stage).

@@

A few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$). The main results reported here were obtained with a conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e. "ideal" dataset).

@@

For WD, Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits. Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions. 
For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig. \ref{fig:fig3} b, model fit not improved when stage was incorporated). Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 2 respectively), meaning a good consistency in the coefficient reported for each stage across studies.

@@

As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero). Hovever, the correlation between seed mass and RGR at adult and saling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig. \ref{fig:fig3} c). Again we could not distinguish between these alternatives. But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicate.

@@

\subsection*{Results from a more complete dataset}

We also reported results from a more complete dataset to determine if additional data could reinforce some of our conclusions. This ''complete'' dataset included correlations measured with both absolute and relative growth rate (Fig. \ref{fig:fig4}), across at least two species, and did not required any control for the source of trait or growth (i.e. both could be measured on different stages) and for the environemental conditions. This release of criteria enlarged in a considerable extent the number of replicates ($n = 216$).

The ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD, Hmax and seed mass, and led to similar conclusions (Fig. \ref{fig:fig4}). For Aarea, additional replicates from the ''complete'' dataset allowed to compare the effect size across plant stage. The results were consistent with a positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).

@@

Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}). The impact of publication bias was probably trivial (Appendix E, Fig. \ref{fig:figA7}). The extent of heterogeneity was high, but was substantially explained by the plant stage effect for SLA and SM, as expected (Appendix E). Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig. \ref{fig:figA9}).

@@

For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model. This is coherent with the mechanisms through which traits affect growth being correctly understood in the model. For SLA and for SM the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation. For WD, Aarea and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.

@@

For seedlings our meta-analyses showed, as expected, a negative relationship between SM and RGR (in mass or height or volume) for small plants, that dissipated as plants grew larger. This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.

For WD the meta-analysis showed negative correlation with RGR across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=2-5). In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.

@@

Meta-analysis showed a positive correlation between Hmax and RGR for adult stage, but not for saplings and seedlings. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates. While our results are consistent with this pattern, a doubt arise about the absence of correlation between growth and Hmax for small plant stature, due to the limited number of replicates for both saplings (n=4) and seedling stages (n=1).

@@

It is notable that the expected correlations between traits and growth do not appear to be much overridden by cross-correlations among different traits. A recurring issue in trait ecology is how many of the observed correlations arise directly from mechanisms, versus how many from secondary cross-correlation. For example, several papers have suggested that correlations between Hmax and growth rate may arise via cross-correlation with other traits such as WD \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}. Similarly, effects of SM on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}. Secondary cross-correlation might also potentially have the effect of suppressing a correlation that would otherwise be present. While such effects may still be observed within individual studies, across the range of studies reported we found that the available data were consistent with predictions arising directly from mechanisms.

@@

Light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}. The authors explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with diameter above 10 cm were pooled as ``adult''.

Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here. Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g. LMR, LAR, NAR). Nevertheless the existing published evidence, even with all its limitations, is consistent with predictions from a simple growth model, and this suggests that species traits can shed light on their growth trajectories, and hence on the changing growth rate rankings across species as individuals become larger.

>>>>

\mstype{Research Article}
\runninghead{Influence of traits on growth changes with size}
\keywords{absolute growth rate, maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, relative growth rate, seed mass, specific leaf area, wood density}

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 268/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate has often been seen as a central element of its ecological strategy, and as ultimately linked to its traits. Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of traits to predict growth.

\item We propose that traits should influence growth in a way that depends on the size of individual plants. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations). To capture the effects of size, we tested for a shift in the direction of correlation between growth rates and traits across three plant stages: seedling, sapling and adult.

\item Results were consistent with predictions. Specific leaf area was correlated with relative growth rate (RGR) in seedling but not in adult plants. Correlations of RGR with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively. Despite the vast litterature on trait and growth, coverage was limited for wood density, seed mass, maximum height and assimilation rate, and additional studies would be helpful for some trait-growth-stage relationships.

\item Synthesis: We show how trait-growth correlations change in a predictable way with plant size. Our understanding of plant strategies should shift away from attributing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.

@@

The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring. An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates of seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}. From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The ``leaf economic spectrum'' \citep{Wright:2004jb} and the ``wood economic spectrum'' \citep{Chave:2009iy} reflect tissue construction costs (for leaf area and for wood volume respectively), trading off with rates of tissue turnover or mortality. It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}. Yet, recently a number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with specific photosynthetic capacity per unit of leaf mass and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, the correlation has mostly been much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}. Size has long been known to play a central role in organismal design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta}. Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}. At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see section ``Theoretical expectations''). While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.

In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass) to investigate:
\begin{enumerate}
  \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') derived from a recently developed mechanistic model \citep{Falster:2011ii}?
\end{enumerate}
We gathered correlation coefficients between traits and growth from studies that gave explicit information about the size or stage of the plants. While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes. We used plant stage (i.e. seedling, sapling and adult) as a surrogate for the effects of plant size. We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.

Meta-analytic approach allows generalization by summarizing and integrating research results across studies, just like large data compilation commonly used in trait ecology. Yet, a specific interest of meta-analytic approach is also to identify key knowledge gaps. Here, we expected a vast literature on trait and growth to be available, but we were uncertain about the representation of all trait-stages combinations. Thus, a goal of our study was also to identify areas of research needed to improve our understanding of the link between trait and growth.

@@

\textbf{H4: The relationship between seed mass and relative growth rate is negative in seedlings, but weakens with increasing size.}

@@

We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is measured. It is uncertain how much this might translate to faster growth in low light. It might greatly depend on the level of light available.

\textbf{Effect on absolute and relative growth rates}
Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR). The choice of the growth measurement is generally confunded with the size of the plant; RGR in mass is mainly used for seedling, and AGR in diameter or height are mainly used for adult. According to the growth model, the predicted relationship between growth and seed mass in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}). The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$. For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used. However RGR and AGR are fundamentaly different for a lot of ecologists. So we adopted a two step approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.

@@

We aimed to identify studies that measured the correlation between five prominent functional traits (SLA, WD, Aarea, Hmax and seed mass) and a growth measurement across species. Our literature search was conducted in two phases.

@@

The Google Scholar database was searched using a range of Boolean search terms for SLA and WD: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''). This keyword search in Google Scholar returned approx. 18900 papers, from which we took the first 750 items when ranked by ``relevance''.
These papers were examined in addition to those discovered in Phase 1. In addition, we gleaned data from other sources, using our own knowledge as researchers in the field (this included adding data from an in-review study by \citeauthor{Gleason:2016}). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

Overall, we recorded coefficient correlations for a list of 19 traits (Fig. \ref{fig:fig1}): the five for which we had prior expectations, plus 14 others commonly used in the trait literature. SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}. According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits was captured by a search on SLA and WD.

@@

In addition to the chosen criteria for the meta-analyses, the growth measurement used (relative growth rate-RGR or absolute growth rate-AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Thus we stratified the data set into two subsets: one including only studies on RGR, under unstressed conditions and measuring a correlation coefficient at least across 10 species (’ideal’ dataset), and the other set including studies under all conditions (’complete’ dataset). We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for seed mass (i.e. seed stage), or Hmax (i.e. adult stage).

@@

Contrary to our expert expectation, a few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$). The main results reported here were obtained with an even more conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e. "ideal" dataset).

@@

For WD, Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits. Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions. 
For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig. \ref{fig:fig3} b, model fit not improved when stage was incorporated). Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 1 respectively), meaning a strong correlation and /or a good consistency in the coefficient reported for each stage across studies.

@@

As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero). Hovever, the correlation between seed mass and RGR at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig. \ref{fig:fig3} c). Again we could not distinguish between these alternatives. But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.

@@

\subsection*{Results with an inclusive approach}

We also reported results from a more complete dataset, to determine if additional data could reinforce or in contrast overcast some of our conclusions. This ''complete'' dataset included correlations measured with both absolute and relative growth rate (Fig. \ref{fig:fig4}), across at least two species, and did not required any control for the source of trait or growth (i.e. both could be measured on different stages) and for the environemental conditions. This release of criteria enlarged in a considerable extent the number of replicates ($n = 216$).

The ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD, Hmax and seed mass, and led to similar conclusions (Fig. \ref{fig:fig4}). This supports the robustness of the analysis using the conservative approach ('ideal dataset'). For Aarea, additional replicates from the ''complete'' dataset allowed to compare the effect size across plant stage. The results were consistent with a positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).

@@

Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}). The impact of publication bias was probably trivial (Appendix E, Fig. \ref{fig:figA7}). The extent of heterogeneity was high, but was substantially explained by the plant stage effect for SLA and seed mass, as expected (Appendix E). Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig. \ref{fig:figA9}).

@@

For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model. This is coherent with the mechanisms through which traits affect growth being correctly understood in the model. Other mechanisms could also generated these patterns and we discussed them in the discussion. For SLA the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation. For WD, Aarea, seed mass and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.

@@

For seedlings our study showed, as expected, a negative relationship between seed mass and RGR (in mass or height or volume) for small plants, that dissipated as plants grew larger. This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.

For WD the meta-analysis showed negative correlation with RGR across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5). In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
For seedlings a negative correlation arose regardless wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e. stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.

@@

Meta-analysis showed a positive correlation between Hmax and RGR for adult stage, but not for saplings and seedlings. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates. While the results of the meta-analysis were consistent with the expected pattern for Hmax, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1). Consequently, subsequent research are welcomed to validate this result.

@@

It is notable that the expected correlations between traits and growth do not appear to be much overridden by cross-correlations among different traits. A recurring issue in trait ecology is how many of the observed correlations arise directly from mechanisms, versus how many from secondary cross-correlation. For example, several papers have suggested that correlations between Hmax and growth rate may arise via cross-correlation with other traits such as WD \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}. Similarly, effects of seed mass on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}. Secondary cross-correlation might also potentially have the effect of suppressing a correlation that would otherwise be present. While such effects may still be observed within individual studies, across the range of studies reported we found that the available data were consistent with predictions arising directly from mechanisms.

@@

A lot of biotic and abiotic conditions such as light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}. The authors explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with diameter above 10 cm were pooled as ``adult''.

Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here. Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g. LMR, LAR, NAR). However, the existing published evidence is consistent with qualitative predictions of a simple model that assesses the effects of plant size on growth. Thus, the linkage of growth to the mechanisms outlined here can shed light on tree growth trajectories and the size-dependent effects of functional traits on the changing species growth rate rankings as individuals grow larger.
